A boundary-integral framework to simulate \\ the viscous erosion of a porous medium

### 2018-04-05 docs/methods/erosion_methods.tex
NM

Flow-induced erosion reshapes solid material over a range of scales found in nature, from large-scale land formations \cite{} down to human-scale structures and patterns \cite{}. Though less visible, these same forces are at work at the very smallest of scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms. Motivated by these small-scale applications, we develop here numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow --- the most appropriate regime for groundwater flow and the aforementioned biological examples.

Recent work on in the high-Reynolds regime has highlighted the importance of the feedback between flow and morphology that occurs during erosion \cite{}, as well as related processes such as dissolution \cite{} and melting \cite{}. In such cases, the flow alters the shape of the structure, which in turn modifies the surrounding flow, and so on --- a reciprocal process that can be summarized as `sculpting with flow'~\cite{ristroph2018sculpting}.
The example of an eroding porous medium presents new challenges and opportunities in that multiply connected domains must be considered. Furthermore, the long-range effects of Stokes flow facilitates even stronger coupling between bodies.

@@

%% ORIGINAL %%%
\vsp{5}
%sand dunes to be  longer on the windward side~\cite{han1969}, 
%stream-bed erosion is responsible for branching structures of rivers~\cite{coh-dev-sey-yi-szy-rot2015}.  
%Erosion is also important in biophysical applications---plaque erosion in arteries is key to understanding heart disease~\cite{sha2002, gro-gij-van-fer-hat-van-yua-wen2007}, and the separation of biofilms can be explained by erosion~\cite{pic-van-hei2000}.

Recent work has been devoted to understanding fundamental aspects of the fluid-structure interaction that occurs during the erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, mit-spa2016, hewett2017evolution, moore2017riemann, lachaussee2018competitive, lopez2018cfd}, and related processes like dissolution or melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, yuan2017dynamics, claudin2017dissolution, hewett2017pear}.

>>>>

Flow-induced erosion reshapes solid material over a range of scales found in nature, from large-scale land formations \cite{han1969, coh-dev-sey-yi-szy-rot2015} down to human-scale structures and patterns \cite{daerr2003erosion}. Though less visible, these same forces are at work at the very smallest of scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms \cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}. Motivated by these small-scale applications, we develop here numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow --- the most relevant regime for groundwater flow and the aforementioned biological examples.

Recent work on in the high-Reynolds regime has highlighted the importance of the feedback between flow and morphology that occurs during erosion \cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, moore2017riemann}, as well as during related processes such as dissolution and melting \cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion}. In such cases, the flow alters the shape of the structure, which in turn modifies the surrounding flow, and so on --- a reciprocal process that can be summarized as `sculpting with flow'~\cite{ristroph2018sculpting}.
The example of an eroding porous medium presents new challenges and opportunities in that multiply connected domains must be considered. Furthermore, the long-range effects of Stokes flow facilitates even stronger coupling between bodies.

@@

% Other possible refs for erosion: mit-spa2016, hewett2017evolution, moore2017riemann, lachaussee2018competitive, lopez2018cfd

% Other possible refs for dissolution/melting: yuan2017dynamics, claudin2017dissolution, hewett2017pear

%% ORIGINAL %%%
\vsp{5}
